\section*{Abstract}

This whitepaper outlines the development of a \ac{PoC} to integrate a \ac{LLM} extension into the Champions Circle software at SAP Labs India. 
The Champions Circle platform recognizes and rewards employees for exceptional achievements, but its recommendation process is manual and time-intensive. 
The proposed \ac{LLM} extension streamlines this process by evaluating recommendations at the initial stage, providing scores and explanatory feedback to assist decision-making.
    
The \ac{PoC} involved creating a test environment using modern web technologies like Vite, Node.js, and JavaScript, alongside simplified criteria and questions stored in \texttt{.csv} files. 
By dynamically adjusting questions based on selected categories and integrating \ac{LLM} functionality via prompt engineering, the system delivered accurate evaluations. 
The results demonstrated the \ac{LLM}'s ability to assess achievements effectively while adhering to predefined inclusion and exclusion criteria.
    
Key findings highlighted the importance of well-defined criteria, iterative prompt refinement, and dynamic interfaces in enhancing evaluation accuracy and user experience. 
Future steps include expanding criteria, transitioning to SAP UI5 and CAP for production integration, refining prompt engineering with diverse temperature settings, and conducting comprehensive testing.
    
This \ac{PoC} represents a scalable and innovative approach to optimizing achievement evaluations, ensuring fair and efficient recognition processes for the Champions Circle platform.
    